Hierarchy Builder

### 2020-04-27 coqws/easychair.tex
spacing + missing property in Abelian groups

\begin{wrapfigure}[0]{r}{.4\textwidth}
  \includegraphics[width=.4\textwidth]{diagram.pdf}
  %\caption{The hierarchy}
  %\label{fig:hierarchy}
\end{wrapfigure}
\
\begin{coqcode}
HB.mixin Record AbelianGrp_of_CMonoid A of CMonoid A := {
  opp : A -> A;
  addNr : left_inverse zero opp add; (* add is available here *)
}.

@@

>>>>

\begin{wrapfigure}[0]{r}{.4\textwidth}
  \includegraphics[width=.4\textwidth]{diagram.pdf}
  %\caption{The hierarchy}
  %\label{fig:hierarchy}
\end{wrapfigure}
\
\begin{coqcode}
HB.mixin Record AbelianGrp_of_CMonoid A of CMonoid A := {
  opp   : A -> A;
  addNr : left_inverse zero opp add; (* add is available here *)
  addrN : right_inverse zero opp add;
}.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "easychair.tex"
%%% TeX-command-extra-options: "-shell-escape"
%%% ispell-local-dictionary: "english"
%%% End:
